---
title: "Data cleaning"
author: "Kristy Robledo"
date: "04/06/2020"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(janitor)
library(haven)
library(ViewPipeSteps)
library(readxl)
library(ggbeeswarm)
```

## Read in data

```{r}
trt<-read_sas("T:\\ECHO\\Clean\\trt.sas7bdat") %>%
  clean_names() %>%
  remove_constant()

glimpse(trt)
```

## Patients summmary

```{r, echo=TRUE}

trt %>%
  tabyl(subjectkey) ->pids

nrow(pids)
min(pids$n)
max(pids$n)

pids %>%
  ggplot(aes(x=subjectkey, y=n))  +
  geom_bar(stat = "identity")
```

## Drugs

Types of drugs

```{r}
trt %>%
  tabyl(exttreat)
```

Patients with no drug name

```{r}
trt %>%
  filter(is.na(exttreat)) %>%
  select(subjectkey, exttreat, extfdat)
```


## Dates

Find missing dates

```{r}
trt %>%
  filter(is.na(extfdat)) %>%
  select(subjectkey, exttreat, extfdat)
```

Plot dates to check 

```{r}
trt %>%
  ggplot(aes(x=subjectkey, y=extfdat)) +
  geom_point()
```

## Doses

Find missing doses

```{r}
trt %>%
  filter(is.na(extdose)) %>%
  select(subjectkey, exttreat, extdose)

```

Summarise doses by drug type

```{r}
trt %>%
  filter(is.na(extdose)==FALSE) %>%
  group_by(exttreat) %>%
  summarise(n=n(), 
            mean(extdose), 
            median=median(extdose),
            min=min(extdose), 
            max=max(extdose))
```

Plot with a bit of noise - I prefer beeswarm to jitter!

```{r}
trt %>%
  ggplot(aes(x=exttreat, y=extdose, colour=factor(exttreat))) +
  geom_point()+
  geom_quasirandom()

trt %>%
  ggplot(aes(x=exttreat, y=extdose, colour=factor(exttreat))) +
  geom_point()+
  geom_jitter()

```

## long

Make your data 'longer'

```{r}
trt %>%
  select(exttreat, extdose) %>%
  pivot_longer(everything(), names_to="column", values_to="data") ->long
```


## wide

This also performs a function at the same time!

```{r}
trt %>%
  select(subjectkey, exttreat, extdose) %>%
  pivot_wider(names_from = exttreat, 
              values_from = extdose, 
              names_prefix="drug",
              values_fn=mean) ->meandoses
```


## Recode factors levels

```{r}
glimpse(trt)

trt %>%
  mutate(drug = recode(exttreat, `1`="Drugname", `2`="Drugname2")) -> newtrt

newtrt %>%
  tabyl(drug, exttreat)

```

Change continous to categorical

```{r}


trt %>%
  mutate(catdose = ifelse(extdose>=100,"High", "Low")) ->catdat

```


## Change case of character variable

`toupper` and `tolower` functions

```{r}
trt %>%
  mutate(newreason = toupper(extdelro)) ->uppercase
```




## Excel error on read in of dataset

```{r}

df<-read_xlsx("Y:\\Statistics\\Kristy\\for tony\\Laima\\Data\\PAVANI CADMS 20171031.xlsx", sheet = "FinalData")

```

