---
title: "Statistical report for penguin trial"
author: "Kristy Robledo"
date: "16/12/2021"
output: 
    bookdown::word_document2:
      toc: true
    bookdown::pdf_document2:
      toc: true
    bookdown::html_document2:
      toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
library(tidyverse)
library(gtsummary)
library(flextable)
library(palmerpenguins)

#use janitor package and clean_names function for excel!
```

# Statistical report

This is a trial about penguins. **yay**

We are aiming to 

- show
- lots
- of 
- things
- in 
- rmarkdown



## Baseline characteristics

The baseline characteristics are in Table \@ref(tab:base). Also see Figure \@ref(fig:flipper)

```{r base, tab.cap="Baseline characteristics of penguin types", }

penguins %>%
  tbl_summary(by = species) %>%
  as_flex_table()

```



```{r flipper, fig.cap="Flipper length by bill length"}
penguins %>%
  ggplot(aes(x=flipper_length_mm, y=bill_length_mm, colour=species)) +
  geom_point()
```

# Resources

[Bookdown](https://bookdown.org/yihui/bookdown/)


## Reproducibility 

Analyses and summaries produced in this report were carried out using the R statistical environment, version `r paste(version$major, version$minor, sep=",")`. The report itself was produced using an Rmarkdown workflow, located here: `r knitr::current_input(dir = TRUE)``. The following table lists the non-base R packages used in analyzing and building this report.  


```{r tab.cap = "R packages used in analyses and reporting"}
sessioninfo::package_info() %>%
  unclass() %>%
  as_tibble() %>%
  filter(attached==TRUE) %>%
  select(package, ondiskversion, date) %>%
  rename(version=ondiskversion) %>%
  flextable() %>%
  autofit()
  
```


