---
title: "Show and tell"
author: "Kristy Robledo"
date: "27/08/2020"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Table One (Malcolm)


```{r, eval=FALSE}
library(Gmisc)
?getDescriptionStatsBy
```

more information here on how to create tables like this:
https://www.ahajournals.org/doi/full/10.1161/CIRCIMAGING.115.003643

http://gforge.se/2014/01/fast-track-publishing-using-knitr-part-iv/
https://cran.r-project.org/web/packages/Gmisc/vignettes/Descriptives.html

Other useful table one packages are:

```{r, eval=FALSE}

library(Publish)
?utable

library(tableone)
?tableone

library(papaja)
?apa_table


```


# knitr::spin() function  (Mason)

https://bookdown.org/yihui/rmarkdown-cookbook/spin.html

Basically take an R script and turn into a .rmd 'magically' - and can even use Roxygen code to translate in the script to Rmd. 
eg. #+ is a header


```{r, eval=FALSE}
knitr::spin("script.R",knit=FALSE) 
```

Knit=FALSE means it gives the Rmd file.

# creating template code in R (Sol)

For each variable, creates a line of code with the variable name and type:

```{r, eval=FALSE}
for (i in 1:nrow(infant_variable_list) ){
  cat(noquote(paste0("dataset_mod <- dataset_mod %>% mutate( ", infant_variable_list$variables[i], " = dataset$", infant_variable_list$variables[i], " %>% ", infant_variable_list_category$category[i]  ,") \n" )))
}

```

Sol also brought up regular expressions! Something I often forget about. see more here: https://www.rexegg.com/regex-quickstart.html


# Using broom to create tidy outputs (Kristy)

first some data prep:

```{r}
library(tidyverse)
library(broom)
library(flextable)

data(iris)

##create an outcome
df <-iris %>%
  mutate(outcome = case_when(Petal.Width>2 ~1,
                             TRUE ~0))
```

Then we run a model: 

```{r}
model<-glm(outcome ~ Sepal.Length+Sepal.Width, data=df,
            family = binomial(link="logit"))
```

and normally would create output like this:

```{r}
summary(model)
```

But, we can `tidy` this output, and exponeniate it, get the 95% CI and put it in a nice table really easily:

```{r}
broom::tidy(model, exponentiate=TRUE, conf.int=TRUE) %>%
  flextable::flextable() %>%
  flextable::colformat_num(digits=3)
```



