---
date: "Last compiled on `r format(Sys.time(), '%d %B, %Y')`"
author: "Kristy Robledo"
title: "Statistical Report for the EXAMPLE trial"
output: 
  officedown::rdocx_document:
    reference_docx: template.docx 
    page_margins:
      bottom: 1
      top: 1
      right: 1
      left: 1
      header: 0.5
      footer: 0.5
      gutter: 0

knit: (function(inputFile, encoding) {rmarkdown::render(inputFile, encoding = encoding, output_file = paste0("EXAMPLE-statistical-report-", Sys.Date(),".docx")) })
---

```{r setup, include=FALSE}
## setup chunk

knitr::opts_chunk$set(echo = FALSE, fig.cap = TRUE)

##read in packages for reporting
library(officedown)
library(officer)
library(flextable)
library(sessioninfo)

## read in packages for analyses
library(tidyverse)
library(gtsummary)
library(ggsurvfit)

####  formatting helpers  ###################################################################


fp <- fp_par(                                         ##underline
  text.align = "center", 
  padding.bottom = 20, padding.top = 120, 
  border.bottom = fp_border())

ft <- fp_text(shading.color='#EFEFEF', bold = TRUE)   ##format text

ft_title <- fp_text(font.size=16,                     ##format a title not in TC
                    font.family = "Calibri",
                    shading.color = "transparent", 
                    bold = TRUE)       


whitespace <- fp_par(                                 ##create whitespace
  text.align = "center", 
  padding = 30, 
)

set_flextable_defaults(font.family = "Calibri", 
                       font.size = 9, 
                       padding=2, 
                       table.layout = "autofit"
                      )

theme_gtsummary_journal(journal = "jama")

####  load data  ###############################################################


#install.packages("ipcwswitch")
library(ipcwswitch)
data("SHIdat")

#glimpse(SHIdat)

#### derive datasets ##########################################################
SHIdat %>%
  mutate(days = case_when(progStatus==1 ~ progDate-as.Date("1jan2012", "%d%b%Y"), 
                          progStatus==0~ as.Date("1jan2016", "%d%b%Y")-as.Date("1jan2012", "%d%b%Y")) ) ->survdf


```


\newpage

`r ftext("Table of contents", ft_title)` 

<!---BLOCK_TOC--->

## List of figures

<!---BLOCK_TOC{seq_id: 'fig'}--->

## List of tables

<!---BLOCK_TOC{seq_id: 'tab'}--->


\newpage

# Formatting in Rmarkdown

check out the cheatsheets under help>cheatsheets

# Baseline

Check out [this presentation](http://www.danieldsjoberg.com/gtsummary-weill-cornell-presentation), or one of my previous sessions about gtsummary and its fantastic functions. 

```{r, tab.id = "base", tab.cap = "Baseline characteristics by treatment"}
SHIdat %>%
  select(agerand, bras.f, sex.f, tt_Lnum, pathway.f) %>%
  tbl_summary(by = bras.f, 
              label = list(agerand ~ "Age at randomisation in years"),  ##add nicer names
              statistic = list(agerand ~ "{mean} ({sd})",               ##change which stats are shown
                               tt_Lnum ~ "{median} ({min}-{max})"), ) %>%
  add_overall() ->t1  ##add overall column

t1 %>%
  as_flex_table()    ##output as flextable so it comes out nicely. If you dont go this, you will just get a warning that they have automatically applied flextable to your table
```



\newpage

# Cox regression analysis

Method: cox regression for the effect of treatment. 

We plan to adjust for 

- list1
- list2

```{r, tab.id = "cox", tab.cap = "COx regression analysis for PFS"}
coxph(Surv(days, progStatus)~bras.f + agerand, data=survdf) %>% ##run your model
  tbl_regression(exponentiate = TRUE) %>%                       ##format nicely
  as_flex_table()

```



# Kaplan-Meier curves
<!---BLOCK_LANDSCAPE_START--->
```{r, fig.cap="PFS by treatment", fig.dim=c(10,5.5)}

br<-seq(0, 365*5, by=365)

survdf %>%
  survfit2(Surv(days, progStatus) ~ bras.f, .) %>%
  ggsurvfit() +
  labs(x= "Years from randomisation", 
       y="PFS") +
  add_risktable() +
  scale_ggsurvfit(x_scales = list(breaks = br, 
                                  labels = round(br/365, 2)))

```
<!---BLOCK_LANDSCAPE_STOP--->


## Survival at time t (or find time for probability p eg. median survival)

```{r, tab.id="tblsurv", tab.cap="Survival table"}

survdf %>%
survfit2(Surv(days, progStatus) ~ bras.f, .) %>% 
  tbl_survfit(times=c(365,365*2),
              label_header = "**{time} days**") %>%
  as_flex_table()
```

`r whitespace`


# Crossreferencing 

Take a look at Table \@ref(tab:base) for baseline and Table \@ref(tab:cox) for the regression. 


# Inline reporting

There are a total of `r nrow(SHIdat)` participants enrolled in this trial. 
The average age is `r mean(SHIdat$agerand, na.rm=TRUE)`. Obviously you would also want to round this number....

Or we can use gtsummary helper "inline_text" function if you have saved the table. For example, the mean age is `r inline_text(t1, variable = agerand, column='stat_0')` years. 


# AE tables

- look to `gtreg` package and `tbl_reg`. Presentation and [examples here](https://shannonpileggi.github.io/gtreg/)


\newpage

# Reproducibility receipt

Analyses and summaries produced in this report were carried out using the R statistical environment, version `r paste(version$major, version$minor, sep=".")`. The report itself was produced using an Rmarkdown workflow, located here: `r knitr::current_input(dir = TRUE)``. The following table lists the non-base R packages used in analyzing and building this report.  


```{r, tab.cap = "R packages used in analyses and reporting"}
sessioninfo::package_info() %>%
  unclass() %>%
  as_tibble() %>%
  filter(attached==TRUE) %>%
  select(package, ondiskversion, date) %>%
  rename(version=ondiskversion) %>%
  flextable()
  
```

